Rapid cycleway prioritisation tool

### 2020-05-30 code/index.Rmd
Fix edge case where la not in region

```{r, eval=FALSE}
dir.create(dn)
region_names_to_build = regions$Name
region_names_to_build = regions$Name[!regions$html_name %in% built_regions]
# sample_to_build_regex = "west of|west y|west mid|hereford|nott|leic|manc|liv|cam"
# region_names_to_build = regions %>% 
#   filter(grepl(pattern = sample_to_build_regex, x = Name, ignore.case = TRUE)) %>% 
#   pull(Name)
# region_names_to_build = c("West Yorkshire", "Nottingham")
# region_names_to_build = c("Greater London", "Cambridgeshire")
regions_within_names = c("Leicester", "Nottingham", "Derby", "Stoke-on-Trent")
names(regions_within_names) = c(paste0(regions_within_names[1:3], "shire"), "Staffordshire")
regions_containing_names = names(regions_within_names)
names(regions_containing_names) = regions_within_names

>>>>

```{r, eval=FALSE}
dir.create(dn)
region_names_to_build = regions$Name
# region_names_to_build = regions$Name[!regions$html_name %in% built_regions]
# sample_to_build_regex = "west of|west y|west mid|hereford|nott|leic|manc|liv|cam"
# region_names_to_build = regions %>% 
#   filter(grepl(pattern = sample_to_build_regex, x = Name, ignore.case = TRUE)) %>% 
#   pull(Name)
# region_names_to_build = c("West Yorkshire", "Nottingham")
# region_names_to_build = c("Greater London", "Cambridgeshire")
regions_within_names = c("Leicester", "Nottingham", "Derby", "Stoke-on-Trent")
names(regions_within_names) = c(paste0(regions_within_names[1:3], "shire"), "Staffordshire")
regions_containing_names = names(regions_within_names)
names(regions_containing_names) = regions_within_names
